Neural correlates of the deployment of spatial attention, and their modulation by repetitive movements

### 2024-09-28 manuscript.qmd
Debugging crash
Added download code for eyetracking data

if (processdata<2){
  # download processed data if missing
  if (!file.exists('local/Expt1resps.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Expt1resps.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/Expt2resps.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Expt2resps.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/Exp1Group.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp1Group.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2Group.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2Group.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2GroupStim.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2GroupStim.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2GroupNoStim.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2GroupNoStim.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}  
}

>>>>

if (processdata<2){
  # download processed data if missing
  if (!file.exists('local/Expt1resps.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Expt1resps.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/Expt2resps.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Expt2resps.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
  if (!file.exists('local/Exp1Group.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp1Group.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2Group.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2Group.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2GroupStim.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2GroupStim.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')}
    if (!file.exists('local/Exp2GroupNoStim.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('Exp2GroupNoStim.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')} 
      if (!file.exists('local/eyepositions.RData')){
osfproject <- osf_retrieve_node("dns89")
osffiles <- osf_ls_files(osfproject,n_max=300)
fid <- pmatch('eyepositions.RData',osffiles$name)
osf_download(osffiles[fid,],path='local/')} 
}
